\chapter{Introduction}

\newcommand{\docite}{\textcolor{red}{~█}}

Quantum mechanics has expanded the scope of physics, where a new way of thinking about atomic and photonics models emerged and new theories of microscopic effects are still researched experimentally and theoretically.
Nowadays, within the realm of quantum research, atoms are being controlled in an isolated environment, that have allowed to set e.g.\ new high-precision time standards~\cite{Brewer2019} and resolve new types of matter~\cite{Anderson1995, Davis1995}. The scope of these studies has greatly expanded over the last 30 years, as laser-cooling, trapping, and detection techniques have gained momentum. Within this realm, the field of quantum simulation is of particular interest to this thesis, where microscopic effects found in solid state physics are modelled by arranging and interacting atoms on a scale much larger than they appear in nature and can therefore be studied in detail. Forming the structures necessary to measure effects in this macroscopic regime, such as Ising~\cite{Schauß2015} or Hubbard~\cite{Boll2016} models, is achieved by confining atoms to periodic potential wells in optical lattices.

Advancements in detection of atoms have led to quantum gas microscopes~\cite{Bakr2009, Sherson2010}, where single-site resolution in these lattices is possible and are thus a perfect fit for use in quantum simulators, as interactions and correlations between atoms can be studied in detail. This has allowed to measure e.g.\ superfluid to Mott insulator transitions~\cite{Sherson2010} or antiferromagnetic correlations~\cite{Boll2016}. However, control over these systems was limited in the past, as optical lattices have a fixed geometry and cycle times were long due to the necessity of cooling atoms to ultra-cold temperatures. More recently however, optical tweezers have emerged~\cite{Lee2016, Barredo2016, Endres2016, Norcia2018}, where each lattice site is generated from an individual laser beam. This allows high control and tunability not only between lattice sites, but also poses the ability to generate arbitrary geometries. As these traps can be made sufficiently deep, this removes the requirement of cooling atoms to ultra-cold temperatures, resulting in fast cycle times.

To study manybody effects in these optical tweezers, Rydberg atoms can be employed. They offer the ability of long-range interactions on a micrometer scale~\cite{Urban2009} and therefore across multiple tweezers. Direct manybody-effects are seen as part of the Rydberg blockade, where within a certain radius, only a single atom can be excited into a Rydberg state. However Rydberg atoms are very well suited to study spin Hamiltonians, which are used to research quantum magnetism~\cite{Kiffner2017}. In combination with optical tweezers, coherent dynamics can be observed, as the positions of atoms aren't random. This has allowed for example, to observe coherent excitation hopping in spin-flip Hamiltonians~\cite{Barredo2015} and large arrays of Rydberg atoms modelling Ising dynamics~\cite{Labuhn2016}. In another approach, out-of-time order correlators are a measure of chaotic behaviour in condensed matter physics and can be modelled in spin-like systems~\cite{Fan2017}. Quantum manybody dynamics in spin-models have also been observed using a programmable 1D quantum simulator, where symmetry breaking across phase transitions was detected~\cite{Bernien2017}.

This forms the building blocks for the experiment this thesis is a part of. Hereby, single Potassium-39 atoms are trapped in optical tweezers and excited to Rydberg levels~\cite{Hirthe2018}. The tweezers are generated through \acp{slm}~\cite{Osterholz2020}, where arbitrary intensity patterns are formed and projected onto the atomic cloud.


This work presents three new setups towards this experiment. In Chapter~\ref{ch:chopping}, loading of potassium atoms from the cloud into tweezers is discussed. The chapter places focus on the theory behind \acp{eom} which is followed by the characterization of two \acp{eom}, that will be used to improve the loading stage of the experiment and allow deploying more tweezers in the future.
Chapter~\ref{sec:sorting} then works towards enabling unity filling in a grid of atoms. For this, a new way of generating the tweezers is introduced in the form of \acp{aod}, which can move atoms into vacancies in the lattice. Therefore the theory behind the deflectors is explained and is followed by comparing two algorithms of achieving this sorting of atoms. The chapter is then concluded by describing the driver used for the dynamic tweezers and ways to work around its limitations.
Finally, Chapter~\ref{ch:spin_resolved} presents a spin-selective imaging approach by applying dynamic tweezers that are sensitive to only one spin species using the same \acp{aod} as above. The spin-sensitive laser used in this setup was built during this thesis and is concluded with the characterization of this laser.
